\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This document provides a template for a project report along with guidelines on how to write a report. It also includes several useful examples to help you become accustomed to \LaTeX. The number and titles of the chapters may vary depending on the type of project and individual preferences. The section titles presented here are only illustrative and should be adapted as necessary. Likewise, the number of sections within each chapter remains flexible. This template may or may not suit your project, so it is advisable to discuss the structure of your report with your supervisor.

\medskip

\noindent\textbf{Guidelines for writing an abstract:}  
The abstract is a summary of the report, presented in a single paragraph and not exceeding 250 words. It must be \textit{self-contained} and should not refer to other sections, figures, tables, equations, or references. In general, an abstract comprises four key elements:
\begin{enumerate}
    \item \textbf{Introduction} (background and purpose of the project);
    \item \textbf{Methods} (experiments, techniques, or implementation);
    \item \textbf{Results} (main conclusions obtained, along with their significance);
    \item \textbf{Conclusions} (implications for the field of study).
\end{enumerate}
The distribution of these four parts should reflect their relative importance within the body of the report. The abstract begins with a few sentences describing the general theme and main objective of the project, then presents the targeted problem. This is followed by a brief description of the methodology employed, before summarizing the results obtained and their meaning. Finally, the conclusion highlights the project’s major contributions and its impact on the field.

\vspace{1cm}
\noindent
\textbf{Keywords:} Up to five keywords or key phrases, separated by commas

\vfill

\noindent
\textbf{Report's Total Word Count:} The word count must be stated after the abstract. 
The report should contain at least 10,000 words and at most 15,000 words (counting from Chapter 1 
through the end of the Conclusions chapter, but excluding the list of references, appendices, abstract, 
and text contained in figures, tables, listings, and captions), roughly 40 to 50 pages.

\medskip

\noindent
\textbf{The project's source code must be uploaded to GitLab. The GitLab link should be included here, following the word count.}

\medskip

\noindent
The report (preferably in PDF format) must be submitted via the "Ecampus" platform before the deadline. 
If a student has resit examinations for any taught modules, the submission deadline for the dissertation 
will be postponed by two weeks from the original deadline.
